MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-03-12 MAESTROeX_I/paper.tex
point to XRB_III for Godunov details

The construction of face-centered time-centered states used to discretize the
advection terms for velocity, species, and enthalpy, are performed using
standard multidimensional corner transport upwind 
\cite{colella1990multidimensional,saltzman1994unsplit} with piecewise-parabolic
one-dimensional tracing \cite{colella1984piecewise}.  In this step,
using equation (\ref{eq:momentum}), 
we compute time-centered edge velocities, $\uadvonedag$, using
$\Ub^n$.  The $\dagger$ superscript refers to the
fact that the predicted velocity field does not satisfy the divergence
constraint.  We then construct $\uadvone$ from $\uadvonedag$
using a MAC projection.
We note that $\uadvone$ satisfies the divergence constraint
\begin{equation}
\nabla \cdot \left(\beta_0^n \uadvone\right) = \beta_0^n \left(S^{\nph,\star} - \frac{1}{\gammaonebar^np_0^n}\frac{\partial p_0}{\partial t} \right).
\end{equation}
In practice we solve for.

@@

\item Compute the time-centered species edge states, $(\rho X_k)^{\nph,\pred}$,
  for the conservative update of $(\rho X_k)^{(1)}$ using
  $\Ub = \uadvone$ and $\rho_0^n$.
\MarginPar{We may not need $\rho_0$ if we predict $\rho X$ or $\rho$ and $X$.  AJN: If we end up keeping prediction of $\rho'$ and $X$, and $(\rho h)'$ we need to summarize this, particularly since $\rho_0$ and $(\rho h)_0$ treatment differs from previous papers.}

@@

\item Compute the time-centered enthalpy edge state, $(\rho h)^{\nph,\pred},$
  for the conservative update of $(\rho h)^{(1)}$
  using $\Ub = \uadvone$ and $(\rho h)^n$,

@@

The procedure to construct $\uadvtwodag$ is identical to the procedure
for computing $\uadvonedag$ in {\bf Step 3}, but uses
the updated value $S^{\nph}$ rather than $S^{\nph,\star}$.
We note that $\uadvtwo$ satisfies the divergence constraint
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph} \uadvtwo\right) =
\beta_0^{\nph} \left(S^{\nph} - \frac{1}{\gammaonebar^{n+\myhalf}p_0^{n+\myhalf}}\frac{\partial p_0}{\partial t}\right),
\end{equation}
where
\begin{equation}
\beta_0^{\nph} = \frac{ \beta_0^n +  \beta_0^{n+1,\star} }{2},
\qquad
\gammaonebar^{\nph} = \frac{ \gammaonebar^n +  \gammaonebar^{n+1,\star} }{2}.
\qquad
p_0^{\nph} = \frac{ p_0^n + p_0^{n+1,\star} }{2},
\end{equation}

@@

\item Compute the time-centered species edge states, $(\rho X_k)^{\nph,\pred}$,
  for the conservative update of $(\rho X_k)^{(1)}$ using $\Ub = \uadvtwo$ and
  $\rho_0^n$.

@@

\item Compute the time-centered enthalpy edge state, $(\rho h)^{\nph,\pred},$
  for the conservative update of $(\rho h)^{(1)}$.

@@

First, we compute the time-centered edge velocities, $\Ub^{\nph,\pred}$.
Then, we define
\begin{equation}
\rho^\nph = \frac{\rho^n + \rho^{n+1}}{2}, \qquad \rho_0^\nph = \frac{\rho_0^n + \rho_0^{n+1}}{2}.
\end{equation}
We update the velocity field $\Ub^n$ to $\Ub^{n+1,\dagger}$ by discretizing
equation (\ref{eq:momentum}) as
\begin{equation}
\Ub^{n+1,\dagger}
= \Ub^n - \dt \left[\uadvtwo \cdot \nabla \Ub^{\nph,\pred} \right]
 - \dt \left[ \frac{1}{\rho^\nph} \nabla \pi^\nmh + \frac{\left(\rho^\nph-\rho_0^\nph\right)}{\rho^\nph} g^{\nph} \eb_r \right],
\end{equation}
Again, the $\dagger$ superscript refers
to the fact that the updated velocity does not satisfy the divergence
constraint.

>>>>

The construction of face-centered time-centered states used to discretize the
advection terms for velocity, species, and enthalpy, are performed using
a standard multidimensional corner transport upwind approach
\citep{colella1990multidimensional,saltzman1994unsplit} with piecewise-parabolic
one-dimensional tracing \citep{colella1984piecewise}.  The full details of this
Godunov advection approach for all steps in this algorithm are described 
in Appendix A of \cite{XRB_III}.

In this step, using equation (\ref{eq:momentum}), 
we compute time-centered edge velocities, $\uadvonedag$, using
$\Ub^n$.  The $\dagger$ superscript refers to the
fact that the predicted velocity field does not satisfy the divergence
constraint.  We then construct $\uadvone$ from $\uadvonedag$
using a MAC projection.
We note that $\uadvone$ satisfies the divergence constraint
\begin{equation}
\nabla \cdot \left(\beta_0^n \uadvone\right) = \beta_0^n \left(S^{\nph,\star} - \frac{1}{\gammaonebar^np_0^n}\frac{\partial p_0}{\partial t} \right).
\end{equation}
In practice we solve for.

@@

\item Compute the time-centered species edge states, $(\rho X_k)^{\nph,\pred}$,
  for the conservative update of $(\rho X_k)^{(1)}$ using a Godunov approach \citep{XRB_III}.
\MarginPar{We may not need $\rho_0$ if we predict $\rho X$ or $\rho$ and $X$.  AJN: If we end up keeping prediction of $\rho'$ and $X$, and $(\rho h)'$ we need to summarize this, particularly since $\rho_0$ and $(\rho h)_0$ treatment differs from previous papers.}

@@

\item Compute the time-centered enthalpy edge state, $(\rho h)^{\nph,\pred},$
  for the conservative update of $(\rho h)^{(1)}$
  using using a Godunov approach \citep{XRB_III}.

@@

The procedure to construct $\uadvtwodag$ is identical to the Godunov procedure
for computing $\uadvonedag$ in {\bf Step 3}, but uses
the updated value $S^{\nph}$ rather than $S^{\nph,\star}$.
We note that $\uadvtwo$ satisfies the divergence constraint
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph} \uadvtwo\right) =
\beta_0^{\nph} \left(S^{\nph} - \frac{1}{\gammaonebar^{n+\myhalf}p_0^{n+\myhalf}}\frac{\partial p_0}{\partial t}\right),
\end{equation}
where
\begin{equation}
\beta_0^{\nph} = \frac{ \beta_0^n +  \beta_0^{n+1,\star} }{2},
\qquad
\gammaonebar^{\nph} = \frac{ \gammaonebar^n +  \gammaonebar^{n+1,\star} }{2}.
\qquad
p_0^{\nph} = \frac{ p_0^n + p_0^{n+1,\star} }{2},
\end{equation}

@@

\item Compute the time-centered species edge states, $(\rho X_k)^{\nph,\pred}$,
  for the conservative update of $(\rho X_k)^{(1)}$ usingusing a Godunov approach \citep{XRB_III}.

@@

\item Compute the time-centered enthalpy edge state, $(\rho h)^{\nph,\pred},$
  for the conservative update of $(\rho h)^{(1)}$ using a Godunov approach \citep{XRB_III}..

@@

First, we compute the time-centered edge velocities, $\Ub^{\nph,\pred}$
using a Godunov approach \citep{XRB_III}. Then, we define
\begin{equation}
\rho^\nph = \frac{\rho^n + \rho^{n+1}}{2}, \qquad \rho_0^\nph = \frac{\rho_0^n + \rho_0^{n+1}}{2}.
\end{equation}
We update the velocity field $\Ub^n$ to $\Ub^{n+1,\dagger}$ by discretizing
equation (\ref{eq:momentum}) as
\begin{equation}
\Ub^{n+1,\dagger}
= \Ub^n - \dt \left[\uadvtwo \cdot \nabla \Ub^{\nph,\pred} \right]
 - \dt \left[ \frac{1}{\rho^\nph} \nabla \pi^\nmh + \frac{\left(\rho^\nph-\rho_0^\nph\right)}{\rho^\nph} g^{\nph} \eb_r \right],
\end{equation}
Again, the $\dagger$ superscript refers
to the fact that the updated velocity does not satisfy the divergence
constraint.
